---
title: "Exploratory Analysis"
author: "YZ Analytics"
output: pdf_document
---

```{r}
library(tidyverse)
library(GGally)
```

## Countries 

It will be important to understand the countries that are represented in our dataset in order to be able to know what types of mapping capabilities we have to have to create a good experience. 

```{r}
path <- "../data/winemag-data-130k-v2.csv"
Wine <- read_csv(path,
                 col_types = cols(
                     X1 = col_double(),
                     country = col_character(),
                     description = col_character(),
                     designation = col_character(),
                     points = col_double(),
                     price = col_double(),
                     province = col_character(),
                     region_1 = col_character(),
                     region_2 = col_character(),
                     taster_name = col_character(),
                     taster_twitter_handle = col_character(),
                     title = col_character(),
                     variety = col_character(),
                     winery = col_character()),
                 progress = FALSE
                 ) %>%
    rename(id = X1)
```

```{r}
Wine %>% glimpse()
```

```{r}
top_countries_tbl <- Wine %>%
    mutate(country = fct_explicit_na(country)) %>%
    mutate(country = fct_lump(country, 12)) %>%
    count(country, sort = TRUE) %>%
    mutate(prop = n / sum(n))

top_countries_tbl
```

The top 13 categories, including the lumped-together category of "Other" consist of those categories which have a count consisting of more than 1% of the observations in the dataset. 

```{r}
top_countries_tbl %>%
    mutate(prop_cumulative = cumsum(prop)) %>%
    ggplot(aes(x = seq_along(country), y = prop_cumulative)) +
    geom_point() +
    geom_label(aes(label = country)) +
    scale_y_continuous(limits = c(0, 1)) +
    scale_x_continuous(breaks = seq(0, 13)) +
    labs(x = "# Top Countries" , y = "Cumulative Proportion")
```

Note that most of the observations, in fact, more than 90% of the observations are contained in the 8 most represented countries and 80% on the top 4, and 60% on the top 2 (USA and France). 

It looks like it will be possible to create an interactive map. Now we need to geolocate the wineries. Worst case scenario we have the countries and their representation in the dataset. 

Another interesting fact is that since 40% of the observations come from the USA, then perhaps it will be possible to get historical information to add quantitative predictors to our dataset, but it is not crucial since our focus is in the presentation of the data. 

## Wineries

Is there a similar concentration for the wineries? Turns out no. Lumping won't work because there are just so many wineries and there aren't any ones that particularly dominate. 

```{r}
top_wineries_tbl <- Wine %>%
    count(winery, sort = TRUE) %>%
    mutate(prop = n / sum(n)) %>%
    mutate(prop_cumulative = cumsum(prop)) 

mean_prop <- mean(top_wineries_tbl$prop)
mean_prop

top_wineries_tbl %>%
    ggplot(aes(x = prop)) +
    geom_histogram(bins = 30) +
    geom_vline(xintercept = mean_prop, color = "red")
```

The table below summarizes the information for the proportions of each winery.

```{r}
summary(top_wineries_tbl)
```

From the summary we note that half of the wineries contain more than 90% of the observations, and 25% of the wineries contain more than 70% of the observations. However there are 16757 wineries which means that 25% of the observations is around 4000 wineries. 

If we need to geolocate the wineries and we run into trouble, then perhaps only doing half will suffice for our visualization.

## Variety

Variety of a wine refers to the type of grape that is used - for example, among white grape wines, there are varieties such as Sauvignon Blanc, Chardonnay, and Riesling. Among red grape wines, some varieties include Merlot, Cabernet Sauvignon, and Pinot Noir.

```{r}
top_varieties_tbl <- Wine %>%
    count(variety, sort = TRUE) %>%
    mutate(prop = n / sum(n)) %>%
    mutate(prop_cumulative = cumsum(prop)) 

summary(top_varieties_tbl)

top_varieties_tbl %>%
  arrange(desc(prop)) %>%
  head()
```

We can see from the summary that with among wine variety, 25% of the varieties include more than 97% of of the wines and half of the varieties account for more than 99% of the observed wines. Additionally, Pinot Noir accounts for more than 10% of the wines, followed by Chardonnay with 9.0%, Cabernet Sauvignon with 7.3%, and Red Blend with 6.9%.

## Designation

Designation is a tricky variable to work with. It refers to a label placed on the wine by the winemaker in regulation with rules of the country, although not every country has the same rules. For example, the designation of "Reserve" wine generally means the wine has been set aside to age for a longer time than other wines generally would, and it often implies a higher quality. While "Reserva" refers to reserve wines in Spain, and "Riserva" to those in Italy, the two countries have different rules about how long the wine must be aged for in order to receive their respective designations. Other countries, like the U.S., don't have any rules in general. Given this general lack of universality of designation, this variable likely will not mean much in our project, but we can still look at its characteristics.

```{r}
top_designation_tbl <- Wine %>%
    count(designation, sort = TRUE) %>%
    mutate(prop = n / sum(n)) %>%
    mutate(prop_cumulative = cumsum(prop)) 

summary(top_designation_tbl)

top_designation_tbl %>%
  arrange(desc(prop)) %>%
  head()
```

While 28.8% of the wines do not have a designation, 25% of the designations contain more than 73% of the wines. We see that of the most common 5 designations, three of them are related to reserve wines but in different languages, while the other two refer to estate wines - wines in which the grapes are grown and the wine is made in the same location.

## Taster

The tasters are Wine Enthusiast Magazine wine reviewers.

```{r}
top_taster_tbl <- Wine %>%
    mutate(taster_name = fct_explicit_na(taster_name)) %>%
    mutate(taster_name = fct_lump(taster_name, 15)) %>%
    count(taster_name, sort = TRUE) %>%
    mutate(prop = n / sum(n))

top_taster_tbl
```

While 20% of the wines do not have tasters listed, 19.6% of the wines were tasted by Roger Voss, followed by 11.6% which were tasted by Michael Schachner. A potentially interesting side project could be to try and differentiate the wine descriptions between tasters, or to search for patterns in each taster's preferred wines.

We can speculate if any of the tasters are biased for more positive or negative reviews by looking at mean points per taster:

```{r}
Wine %>%
  group_by(taster_name) %>%
  summarize(meanpoints = mean(points)) %>%
  arrange(desc(meanpoints))
```

The mean points per taster range between 85.9 and 90.6. Although there are likely many factors underlying these differences in points between reviewers, if I were a wine maker, I would want Anne Krebiehl MW or Matt Kettmann reviewing my wine, not Alexander Peartree.

## Points

Points is the variable we will be trying to predict.

```{r}
points_tbl <- Wine %>%
    count(points, sort = TRUE) %>%
    mutate(prop = n / sum(n))

summary(points_tbl)

points_tbl %>%
  ggplot(aes(x = points, y = prop)) +
  geom_bar(stat = "identity")
```

The points look fairly normally distributed - there might be a slight right skew due to very few wines being rated over 95 points. The points range from 80-100 with both mean and median of 90 points.

## Price 

```{r}
price_tbl <- Wine %>%
    count(price, sort = TRUE) %>%
    mutate(prop = n / sum(n)) %>%
    mutate(prop_cumulative = cumsum(prop)) 

summary(price_tbl)
```

We can see from the table that the price for wine ranges between 4 and 3,300 USD. More than 98% of the wines are under 101.20 USD, and more than 99.7% of the wines are less than 203.5 USD.

## Description

Here is an example of the description. 

```{r}
Wine %>% pull(description) %>% pluck(1)
```

This is one example. We will want to extract features from the description in order to incorporate this information into any model we do. 

## Province and Regions

Province and regions are related to country for self-explanatory reasons. Region is a smaller area of a province. Let's just explore province.

```{r}
top_province_tbl <- Wine %>%
    count(province, sort = TRUE) %>%
    mutate(prop = n / sum(n)) %>%
    mutate(prop_cumulative = cumsum(prop)) 

summary(top_province_tbl)

top_province_tbl %>%
  arrange(desc(prop)) %>%
  head()
```

Unsurprisingly, provinces in the U.S., France, and Italy dominate the top provinces list. A whopping 28% of our wines come from California alone.
