---
title: "Text analysis"
author: "YZ Analytics"
date: ""
output: 
  pdf_document:
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r, setup, include=FALSE}
library(mosaic)
library(tm)
library(text2vec)
library(tidytext)
library(forcats)
library(stringr)
```

Calculating Term Frequency and Inverse Document Frequency by points:

Code based from https://www.tidytextmining.com/tfidf.html.

```{r}
Wine_points_tfidf <- Wine %>%
  unnest_tokens(word, description) %>%
  count(points, word, sort = TRUE) %>%
  bind_tf_idf(word, points, n)
```

```{r}
Wine_points_tfidf %>%
  filter(points == 100) %>%
  arrange(desc(tf_idf))
```

We see that the words with the highest TF-IDF values are the unique words in the 100-point wine descriptions that occur only 1-2 in the vocabulary of all the descriptions. 

Let's look specifically at the words with the highest TF-IDF values for 80-point wines:

```{r}
wine_total_words %>%
  filter(points == 80) %>%
  arrange(desc(tf_idf))
```

These words occur more frequently than the words in the 100-point descriptions. However, the frequencies are pretty low. It might be useful to separate points into different levels (perhaps 80-86 is low rating, 97-93 is medium, and 94-100 is high).

```{r}
Wine$rating <- cut(Wine$points,
                   breaks=c(-Inf, 86, 93, Inf),
                   labels=c("low","medium","high"))
```

```{r}
Wine_rating_tfidf <- Wine %>%
  unnest_tokens(word, description) %>%
  count(rating, word, sort = TRUE) %>%
  bind_tf_idf(word, rating, n)
```

```{r}
Wine_rating_tfidf %>%
  filter(rating == "high") %>%
  arrange(desc(tf_idf))
```

We can also look at TF-IDF based on variables other than points. For example, we can look at TF-IDF values based on variety of wine.

```{r}
wine_words <- Wine %>%
  unnest_tokens(word, description) %>%
  count(variety, word, sort = TRUE)
```

```{r}
plot_wine <- wine_words %>%
  bind_tf_idf(word, variety, n) %>%
  mutate(word = fct_reorder(word, tf_idf)) %>%
  mutate(variety = factor(variety, levels = c("Pinot Noir",
                                            "Cabernet Sauvignon", 
                                            "Chardonnay",
                                            "Red Blend", 
                                            "Riesling")))

plot_wine %>% 
  group_by(variety) %>% 
  top_n(15, tf_idf) %>% 
  ungroup() %>%
  mutate(word = reorder(word, tf_idf)) %>%
  ggplot(aes(word, tf_idf, fill = variety)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf") +
  facet_wrap(~variety, ncol = 2, scales = "free") +
  coord_flip()
```

A lot of the words with high TF-IDF values by variety are obvious - for example, the word with the highest TF-IDF value for riesling is "riesling."

Following https://www.kaggle.com/nnnnick/predicting-wine-ratings-using-lightgbm-text2vec:

```{r}
wine_explore <- Wine %>% 
    select(description, points) %>%
    mutate(description = gsub('[[:punct:] ]+',' ',tolower(description)))

words <- str_split(wine_explore$description, ' ')
all_words <- data.frame(points = rep(wine_explore$points, sapply(words, length)), words = unlist(words))
```

```{r}
words_grouped <- all_words %>%
    group_by(words) %>%
    summarize(
        points = mean(points),
        count = n()
    ) %>%
    filter(count > 10) %>%
    arrange(desc(points))

top <- words_grouped[1:10,] %>% cbind(top_bottom = 'top')
bottom <- words_grouped[(nrow(words_grouped) - 9):nrow(words_grouped),] %>% cbind(top_bottom = 'bottom')
top_bottom <- rbind(top, bottom)

ggplot(top_bottom, aes(x = reorder(words, points), y = points, fill = top_bottom)) +
    geom_bar(stat = 'identity') +
    coord_flip() + 
    scale_fill_manual(values = c('#00b4fb', '#fa6560')) + 
    ggtitle('Wine Review Words with the Highest and Lowest Mean Points', subtitle = NULL) +
    xlab('Average Points') +
    ylab('Word') + 
    labs(fill = 'Top or Bottom')
```

