---
title: "Stat-495 Revised Proposal"
author: "Emily Ye & Shukry Zablah"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r, setup, include=FALSE}
require(mosaic)   # Load additional packages here 
library(rtweet)
# Some customization.  You can alter or delete as desired (if you know what you are doing).
trellis.par.set(theme=theme.mosaic()) # change default color scheme for lattice
knitr::opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
```

**Team Name:** YZ Analytics

**Title:** The Life and Times of a Tweet

**Purpose:** As of 2019, Twitter has 330 million monthly active users, and more than 500 million tweets are sent each day (Ling, 2019). How, then, do certain tweets gain traction? The purpose of this project is to track how original tweets travel through retweets and reach their audience. This project would be useful for Twitter users trying to understand the impact they can have through the platform.

**Data:** We will be working with Twitter data, using the package ``rtweet`` (Kearney, 2019) to interact with Twitter's APIs using commands such as `search_tweets`.

For an example of how the `search_tweets` command works, here is how the most recent 200 tweets with the hashtag #ElectionDay can be extracted:

```{r}
election_tweets <- search_tweets(
  "#ElectionDay", n = 200, include_rts = TRUE
)
```

```{r}
ts_plot(election_tweets, by = "secs") + ggplot2::labs(
    title = "Time series plot of election_tweets aggregated by second")
```

The time is in UTC+0 time zone.

**Variables:**

```{r}
names(election_tweets)
```
The `search_tweets` function results in 90 variables, some of which are N/A. The most relevant variables are listed below:

Identifying information of author:

* screen name
* user ID
* number of followers

Engagement of tweet:

* number of favorites
* number of retweets

Tweet content:

* the text of the tweet
* hashtags
* if the tweet has any images, texts, GIFs, videos or other media

Tweet metadata:

* location of tweet 

// sentiment analysis of tweets?

**Model:** Our model aims to predict the number of retweets of a tweet. We are thinking of using a regression tree.

**End Product:** We aim to demo our analyses online with dynamic visualizations. We will display analyses of tweets from a set list of individuals. We also hope to create a web application for users to personalize our analysis to themselves. For example, such a web application could allow a user to type a tweet they want to send, input their follower count, and the app would display their predicted number of retweets.

### References

Kearney, M. W. (2019). rtweet: Collecting Twitter Data. R package version 0.6.9, https://cran.r-project.org/package=rtweet.

Ling, Y. (2019). 10 Twitter Statistics Every Marketer Should Know in 2019. https://www.oberlo.com/blog/twitter-statistics